\section{Introduction}
\label{sec-intro}
Given tweets about six US airlines, the task is to predict whether a tweet contains positive, 
negative, or neutral sentiment about the airline. This is a typical supervised learning task where
 given a text string, we have to categorize the text string into predefined categories.

 Data Analysis aims to analyze the correlation between each attribute and passenger evaluation with given data. And further integrate data, delete irrelevant
  data, unified data values, etc.

  Models and Forecasts aims to use the integrated data to train the relevant models, 
  improve the accuracy, and Predict attitudes for certain given comments.

  In this article, we use multiple models to train the data and make predictions, and
   finally compare multiple models to get the best training model.

\section{Preliminaries} \label{sec-preliminaries}

In the early stage, the existing data were visually analyzed.

First analyze the emotional attitudes of all comments, including positive, negative, and neutral. And make response statistics.

Furthermore, the attitude statistics of different airlines’ comments are made.

After the statistics of different companies, the sentiment statistics of the tweets 
commenting on each company are further carried out.

Finally, the statistics of frequently used high-frequency words are carried out on three attitudes: positive, negative and neutral.

\section{Method} \label{sec-method}


After the preparatory work, the data are further processed.

Processing data independent of results.

Normalization of training data and test data.

Split train and test data.

After the completion of data processing, the model was established using random forest algorithm.

After the data processing is completed, three models of Random Forest, Gradient Boosting, 
and LSTM RNN are used to fit the data, and the results are compared.



%\section{Experiment} \label{sec-experiment}
%After the training of the model, the prediction was made by using the data.


\section{Conclusions} \label{sec-conclusions}

On this issue, the new model is better than the traditional machine learning model.

Pay attention to the adjustment of parameters when training the model.

Other models can be used to further improve accuracy.


\section*{Acknowledgment}

Thanks for the learning opportunities provided by Tulip, 
I grew up rapidly in this period of time. 
Thanks to my tutor for answering questions and puzzles during my study, 
which is my rapid progress. At the same time, I should also like to thank my senior brother, 
sister and classmates for their help. When I am not successful in my study, 
I will lend a helping hand to help me solve problems.

